Mergeable Types

### 2017-02-28 paper/implementation.tex

\begin{wrapfigure}{L}{.5\textwidth}
	\begin{center}
	\includegraphics[scale=0.8]{Figures/partitions}
	\end{center}
	\caption{Network partitions may leave branches $b_1$ and $b_4$ in one
		partition (red background), and branches $b_2$ and $b_3$ in the other (yellow
		background). Since $b_2$ and $b_3$ cannot merge unless $b_1$ and $b_4$ merge
		(Fig.~\ref{fig:legal-extensions}), they cannot communicate among themselves
		even though they are in the same network partition.}
	\label{fig:partitions}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{L}{.5\textwidth}
	\begin{center}
	\includegraphics[scale=0.8]{Figures/partitions}
	\end{center}
	\caption{Network partitions may leave branches $b_1$ and $b_4$ in one
		partition (red background), and branches $b_2$ and $b_3$ in the other
		(yellow background). Since $b_2$ and $b_3$ cannot merge unless $b_1$ and
		$b_4$ merge, they cannot communicate among themselves even though they are in
		the same network partition.}
	\label{fig:partitions}
\end{wrapfigure}
